Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-02-06 reports/manuscript/cover_letter/cover_letter.tex
Change researcher to Fellow in cover letter

\begin{minipage}{0.8\linewidth}
\hspace{1cm}\begin{tabular}{ll}
Ariel Rokem, PhD & \hspace{1cm} Adam Richie-Halford, PhD\\
Research Assistant Professor & \hspace{1cm}  Postdoctoral researcher \\
Department of Psychology & \hspace{1cm} eScience Institute \\
University of Washington & \hspace{1cm} University of Washington
 \end{tabular}
\end{minipage}

>>>>

\begin{minipage}{0.8\linewidth}
\hspace{1cm}\begin{tabular}{ll}
Ariel Rokem, PhD & \hspace{1cm} Adam Richie-Halford, PhD\\
Research Assistant Professor & \hspace{1cm}  Postdoctoral Fellow \\
Department of Psychology & \hspace{1cm} eScience Institute \\
University of Washington & \hspace{1cm} University of Washington
 \end{tabular}
\end{minipage}
